%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%----------------------------------------------------------------------------------------
%    TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Zachary}{Jones}{ % Your name
\urlstyle{same}\href{mailto:zak@newalexandria.org}{zak@newalexandria.org} ||  \href{https://www.twitter.com/invis_insight}{@invis\_insight} ||   \href{https://www.linkedin.com/in/newalexandria}{LinkedIn}/\href{https://www.github.com/NewAlexandria}{Github}/\href{https://www.stackoverflow/story/newalexandria}{SE}: \href{https://www.linkedin.com/in/newalexandria}{newalexandria}
 \\ % Your website, LinkedIn profile or other web address

\href{tel:+1.412.628.0954}{412.628.0954} mobile  ||  220 E. 63rd Street, New York, NY 10065 
}

%----------------------------------------------------------------------------------------
%    LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

%------------------------------------------------

\subsection{Carnegie Mellon}

\descript{BFA; Electronic and Hypermedia}
\descript{HCI (Interface Design, Usability)}
\location{Pittsburgh, PA. May 2000}
VR/AR work, engineering arts,
including acclaimed Stage 3 lab.

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Arizona State University}
\descript{MFA; HCI (Digital Technology)}
\location{Tempe, AZ. May 2007}
AR, HCI, Simulation, 3D/CNC, water.

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Links
%------------------------------------------------

\section{Links} 

Github:// \href{https://github.com/deedydas}{\bf deedydas} \\
LinkedIn:// \href{https://www.linkedin.com/in/debarghyadas}{\bf debarghyadas} \\
YouTube:// \href{https://www.youtube.com/user/DeedyDash007}{\bf DeedyDash007} \\
Twitter:// \href{https://twitter.com/debarghya_das}{\bf @debarghya\_das} \\
Quora:// \href{https://www.quora.com/Debarghya-Das}{\bf Debarghya-Das}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Coursework
%------------------------------------------------

\section{Coursework}

\subsection{Graduate}

Advanced Machine Learning \\
Open Source Software Engineering \\
Advanced Interactive Graphics \\
Compilers + Practicum \\
Cloud Computing

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{Undergraduate}

Information Retrieval \\
Operating Systems \\
Artificial Intelligence + Practicum \\
Functional Programming \\
Computer Graphics + Practicum \\
{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst) }}} \\
Unix Tools and Scripting

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}

\location{Over 5000 lines:}
Java \textbullet{} Shell \textbullet{} JavaScript \textbullet{} Matlab \\
OCaml \textbullet{} Python \textbullet{} Rails \textbullet{} \LaTeX\ \\ 
\location{Over 1000 lines:}
C \textbullet{} C++ \textbullet{} CSS \textbullet{} PHP \textbullet{} Assembly \\
\location{Familiar:}
AS3 \textbullet{} iOS \textbullet{} Android \textbullet{} MySQL

\sectionspace % Some whitespace after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%    RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Personalization Engine for Financial Products}
\descript{| Director of Engineering (CTO)}

\location{Oct 2015 - Dec 2017 | Brooklyn, NY}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Semantic extraction using custom model tree (CoreNLP proved too heavy).
\item NB classifier for extraction outliers. Tag for reinforcement, or auto-publishing
\item NB classifier to categorize product description sentences into semantic groups for personalized / focused UI displays. 
\item Elasticsearch linked-data results (HAML) and grouped search results. (neo4j)
\item Data cleaning and processing of product ETL pipelines.
\item ML admin panels integrated seamlessly into an editorial admin (CMS).
\item Segmentation by cluster analysis (SQL, offline).  Stan test of stream modeling.
\item Data ontology formed via semiotics of consumer financial banking.

\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{PageUI}
\descript{| Co-Founder, CTO}
\location{Jun 2008 - Mar 2009 | Tempe, AZ}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Developed early reactive-JS codebase, and stacked our app/biz on it. 
\item Mozilla went on to support a labs project that was nearly identical, with major adoption. 
\item Usabilty research showed preference over X-marks, which was mainstream.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{HRS}
\descript{| Co-Founder, CTO}

\location{Jan 2006 - Oct 2007 | Vancouver, BC}
\begin{tightitemize}
\item Designed search and matching algorithms for social search.
\item Semantics modeled as state vectors for protocol engineering.  Pre-blockchain.
\item Performed prior-art research and wrote a draft patent. IP law firm counsel.
\item Developed a collaboration-ware app for course software, distance education.
\end{tightitemize}

\sectionspace % Some whitespace after the section


%------------------------------------------------
% Research
%------------------------------------------------

\section{Research}

%------------------------------------------------

\runsubsection{Cloud App Platform}
\descript{| R\&D Engineering}
\location{Jun 2013 - Oct 2015 | New York, NY}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Designed lambda-as-a-service pattern for data-platform strategy.
\item Won trust with executive backers, started working group.
\item Developed patent strategy with chief patent counsel.
\item All of the above at leading Pharma and Financial Data corp.
\end{tightitemize}

\sectionspace % Some whitespace after the section


%------------------------------------------------

\runsubsection{Bardcruft}
\descript{| Situated Media programme}

\location{2004, 2017 | Tempe; NYC}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Design and built a tool for finding similarities in narratives (‘Hero of 100 Faces’)
\begin{tightitemize}
\item Use of ConceptNet, mysql (now RDF4J and SPARQL)
\item Translation of stories into state trajectories and relationship triples
\item Visualization of semantic graph by-concept (scopes/filters)
\item Text annotation GUI for creating new triples.
\end{tightitemize}

\sectionspace % Some whitespace after the section



%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%    SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
\hfill
\begin{minipage}[t]{1\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Research
%------------------------------------------------

\section{Research}

%------------------------------------------------


\runsubsection{Convergance study of CFD + Experimental Data}
\descript{| ASU}

\location{June 2006 - Oct 2009 | Tempe, AZ}
Multiple studies of a non-turbulent vortex hydrodynamic equilibrium.

\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Algorithmic model development in python and CAD machining. 
\item CFD modeling with ANSYS multiphysics. 
\item Quantified comparison k-$\epsilon$ tubulence, reynolds stress, and laminar simulations.
\item Analysis of free-surface experimental model, and simulation data.
\item Platform patent strategy.  Grants. Seed capital raised. Team of world authorities.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{HRS}
\descript{| Co-Founder, CTO}

\location{Jan 2006 - Oct 2007 | Vancouver, BC}
\begin{tightitemize}
\item Designed search and matching algorithms for social search.
\item Semantics modeled as state vectors for protocol engineering.  Pre-blockchain.
\item Performed prior-art research and wrote a draft patent. IP law firm counsel.
\item Developed a collaboration-ware app for course software, distance education.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{TensorVision}
\descript{| ASU, Sponsored Research}

\location{Sept 2005 – May 2006 | Tempe, AZ}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Formulated notation conventions for data navigational affordances.
\item Aimed at creating consistent semantic meaning in 2D and 3D spaces through quantizing hypermedia datasets using mereotopological models.
\item Research into cognitive continuum across haptic and perceptual domains.  
\item Live test subject research, HCI methods.  Patentable, never filed.
\end{tightitemize}

\sectionspace % Some whitespace after the section


%------------------------------------------------

\runsubsection{Biophoton and QED research visualization.}
\descript{| ASU }

\location{Biophoton and QED research visualization | Tempe, AZ}
\begin{tightitemize}
\item Designed codes for conversion of analytical protein data into physical model.
\item Worked with 3D data in PDB and OBJ formats from the wwPDB database.
\item Designed and programmed of 3D computer graphic algorithms in numpy. Averaging of multiple femtosecond datasets from HPCI/MPI simulations.
\item Solid model files for printing via FDM rapid prototyping on Stratasys hardware.
\end{tightitemize}

\sectionspace % Some whitespace after the section


%------------------------------------------------
% Awards
%------------------------------------------------

\section{Awards} 

\begin{tabular}{rll}
2014     & top 52/2500 & KPCB Engineering Fellow\\
2014     & 2\textsuperscript{nd} most points & Google Code Jam, Qualification Round\\
2014     & 1\textsuperscript{st}/50 & Microsoft Coding Competition, Cornell\\
2013     & National & Jump Trading Challenge Finalist\\
2013 & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament \\
2012 & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
2011 & National & Indian National Mathematics Olympiad (INMO) Finalist \\
2010 & National & Comp. Soc. of India's National Programming Contest\\
\end{tabular}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Societies
%------------------------------------------------

\section{Societies} 

\begin{tabular}{rll}
2014 & top 12\%ile & Tau Beta Pi Engineering Honor Society\\
2014 & National & The Global Leadership and Education Forum (tGELF)\\
2012 & National & Golden Key International Honor Society\\
2012 & National & National Society of Collegiate Scholars\\
\end{tabular}

\sectionspace % Some whitespace after the section


%------------------------------------------------



\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}

